---
title: "Reproducible Data Assignment 1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reproducible Data Assignment 1

This assignment will be described in multiple parts. You will need to write a report that answers the questions detailed below. Ultimately, you will need to complete the entire assignment in a single R markdown document that can be processed by knitr and be transformed into an HTML file.

Steps that I took:

I Forked/cloned the GitHub repository created for this assignment.

<https://github.com/rdpeng/RepData_PeerAssessment1>.

I unzipped and loaded the Activity monitoring data into a format suitable for this analysis with the following command in R.

```{r cars}
echo = TRUE
setwd("~/Desktop/Coursera/Reproducible_data/")
activity <- NULL
activity <- read.csv("activity.csv", header = T, sep = ",")
```

### What is the average daily activity pattern?

Make a time series plot (i.e. ðšðš¢ðš™ðšŽ = "ðš•") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?


```{r cars}
echo = TRUE
setwd("~/Desktop/Coursera/Reproducible_data/RepData_PeerAssessment1/")
activity <- NULL
activity <- read.csv("activity.csv", header = T, sep = ",")
```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
