---
title: "Reproducible Data Assignment 1"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Reproducible Data Assignment 1

This assignment will be described in multiple parts. You will need to write a report that answers the questions detailed below. Ultimately, you will need to complete the entire assignment in a single R markdown document that can be processed by knitr and be transformed into an HTML file.

Steps that I took:

I Forked/cloned the GitHub repository created for this assignment.

<https://github.com/rdpeng/RepData_PeerAssessment1>.

I unzipped and loaded the Activity monitoring data into a format suitable for this analysis with the following command in R.

```{r cars}
echo = TRUE
setwd("~/Desktop/Coursera/Reproducible_data/")
activity <- NULL
activity <- read.csv("activity.csv", header = T, sep = ",")
```

####What is mean total number of steps taken per day?

For this part of the assignment, you can ignore the missing values in the dataset.

Calculate the total number of steps taken per day
1. sum steps for each day 

```{r cars}
sum_ea_day <- NULL
echo = TRUE
sum_ea_day <- tapply(activity$steps, activity$date, sum, na.rm=T)
```

Make a histogram of the total number of steps taken each day
```{r cars}
echo = TRUE
hist(sum_ea_day, xlab = "sum of steps each day", main = "Histogram of steps taken each day")
```



Calculate and report the mean and median of the total number of steps taken per day




### What is the average daily activity pattern?

Make a time series plot (i.e. ðšðš¢ðš™ðšŽ = "ðš•") of the 5-minute interval (x-axis) and the average number of steps taken, averaged across all days (y-axis)
Which 5-minute interval, on average across all the days in the dataset, contains the maximum number of steps?


```{r cars}
echo = TRUE
setwd("~/Desktop/Coursera/Reproducible_data/RepData_PeerAssessment1/")
activity <- NULL
activity <- read.csv("activity.csv", header = T, sep = ",")
```


## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
